---
title: "CGMS_Images"
output: html_document
editor_options: 
  chunk_output_type: console
---
## General Import
```{r setup, include = FALSE}
setwd("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables")
library(ggplot2)
library(scales)
library(plyr)
library(dplyr)
library(tidyr)
library(lubridate)
library(forcats)
library(formattable)
library(flextable)
library(kableExtra)
library(pals)
library(DT)
library(viridis)
library(RColorBrewer)

pdf(NULL)

#This sources the data from the data cleanup process including grabbing all the data from the EORES web services
source("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/FlyoutDataCleanup.R")

#This calls all the functions that actually create the flyout tables
source("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/by_sensor.R")

#This sources all the colormatrix functions to apply the different color schemes to the tables
source("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/colormatrix.R")

webshot::install_phantomjs()
```

## Sensor Index
```{r}
# Need to create a list of sensors to index the flyout tables
# The index is in a specific order shown in the mutate(Sensors = factor(Sensors...)) below
sensors<- flyout_clean %>%
  mutate(platform_name = str_replace(platform_name, " - Spacecraft", "")) %>%
  filter(network_acronym == "CGMS") %>%
  filter(grepl("CGMS", platform_deployment_plans)) %>%
  mutate(platform_deployment_plans = sub(".*CGMS Information - ","",platform_deployment_plans)) %>%
  separate(platform_deployment_plans, sep = "[\\|]", c("dep_one","dep_two","dep_three","dep_four")) %>%
  pivot_longer(cols = starts_with("dep_"), names_to = "extra", values_to = "deployment_plans") %>% 
  select(-extra) %>% 
  separate(deployment_plans, sep = ":", c("type", "value")) %>% 
  filter(type == "Sensors") %>%
  mutate(value = trimws(value, "l")) %>%
  pivot_wider(names_from = "type", values_from = "value") %>%
  separate_rows(Sensors, sep = "; ") %>%
  select(Sensors) %>%
  filter(Sensors != "") %>%
  distinct(Sensors) %>% 
  mutate(Sensors = factor(Sensors, levels = c("Microwave Sounder", "Hyperspectral Infrared Sounder", 
                                              "Radio Occultation", "Multi-purpose Meteorological Imager GEO", 
                                              "Multi-purpose Meteorological Imager LEO", "Multi-viewing, Multi-channel, Multi-polarisation imager", 
                                              "Lightning Mapper", "Broadband Short/Long Wave Radiometer", 
                                              "Visible/UV Radiometer", "UV Limb Spectrometer", 
                                              "SWIR Imaging Spectrometer", "Precipitation Radar", 
                                              "Microwave Imager", "Narrow Band Visible & Near Infrared Imager", 
                                              "Radar Altimetry", "Scatterometer", 
                                              "Sub-Millimeter Ice Cloud Imager", "Synthetic Aperture Radar", 
                                              "High Resolution Optical Imager", "Coronograph", 
                                              "EUV Imager", "X-ray Spectrograph", 
                                              "Energetic Particle Sensor LEO & L1", 
                                              "Energetic Particle Sensor GEO - Low energy electrons and protons",
                                              "Energetic Particle Sensor GEO - High energy electrons and protons",
                                              "Energetic Particle Sensor GEO - Very high energy protons",
                                              "Energetic Particle Sensor GEO - Energetic heavy ions",
                                              "Magnetometer", "Plasma Analyzer"))) %>%
  arrange(Sensors) %>% 
  as.data.frame()
```

## Flyout Tables
There are a couple different ways that the data is sorted depending on the preferred order/groupings of sensors in the flout tables.
There are also a couple different color schemes (colormatrix) depending on the sensors and the preferred color groupings by CGMS. There was some specificity involved that made it so certain tables had to have a colormatrix and sorting specifically for them.

```{r}
#Microwave Sounder
#use by_sensor function to grab the sensors identified by the index or sensors created above
dat_fly<-by_sensor_sort2(flyout_clean, sensors[1,1])
x<- dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[1,1],".png")
save_as_image(x, path = file)
```


```{r}
#Hyperspectral Infrared Sounder; Simple colormatrix
dat_fly<-by_sensor_sort2(flyout_clean, sensors[2,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
#    autofit() %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[2,1],".png")
save_as_image(x, path = file)
```


```{r}
dat_fly<-by_sensor_ss(flyout_clean, sensors[3,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix_ro(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix_ro(dat_fly)) %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[3,1],".png")
save_as_image(x, path = file)
```


```{r}
dat_fly<-by_sensor_names(flyout_clean, sensors[4,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix4(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix4(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[4,1],".png")
save_as_image(x,path = file)
```


```{r}
dat_fly<-by_sensor_sort2(flyout_clean, sensors[5,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[5,1],".png")
save_as_image(x, path = file)
```


```{r}
dat_fly<-by_sensor(flyout_clean, sensors[6,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[6,1],".png")
save_as_image(x, path = file)
```


```{r}
dat_fly<-by_sensor(flyout_clean, sensors[7,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix3(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix3(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[7,1],".png")
save_as_image(x, path = file)
```


```{r}
dat_fly<-by_sensor_sort2(flyout_clean, sensors[8,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/Broadband Short_Long Wave Radiometer.png")
save_as_image(x, path = file)
```


```{r}
dat_fly<-by_sensor_sort2(flyout_clean, sensors[9,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/Visible_UV Radiometer.png")
save_as_image(x, path = file)
```


```{r}
dat_fly<-by_sensor_sort2(flyout_clean, sensors[10,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[10,1],".png")
save_as_image(x, path = file)
```



```{r}
#would need to have the EOL for OCO-2 officially changed to include
dat_fly<-by_sensor_sort2(flyout_clean, sensors[11,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[11,1],".png")
save_as_image(x, path = file)
```



```{r}
dat_fly<-by_sensor_sort2(flyout_clean, sensors[12,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[12,1],".png")
save_as_image(x, path = file)
```



```{r}
dat_fly<-by_sensor_sort2(flyout_clean, sensors[13,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[13,1],".png")
save_as_image(x, path = file)
```


```{r}
dat_fly<-by_sensor_sort3(flyout_clean, sensors[14,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[14,1],".png")
save_as_image(x, path = file)
```



```{r}
dat_fly<-by_sensor(flyout_clean, sensors[15,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[15,1],".png")
save_as_image(x, path = file)
```



```{r}
dat_fly<-by_sensor_sort2(flyout_clean, sensors[16,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[16,1],".png")
save_as_image(x, path = file)
```



```{r} 
dat_fly<-by_sensor(flyout_clean, sensors[17,1])
dat_fly$`2022`<-NA
dat_fly$`2023`<-NA
dat_fly$`2024`<-NA
dat_fly<- dat_fly %>% select(Platform, `2022`, `2023`, `2024`, everything())
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[17,1],".png")
save_as_image(x, path = file)
```



```{r}
dat_fly<-by_sensor(flyout_clean, sensors[18,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[18,1],".png")
save_as_image(x, path = file)
```


```{r}
dat_fly<-by_sensor(flyout_clean, sensors[19,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[19,1],".png")
save_as_image(x, path = file)
```



```{r}
dat_fly<-by_sensor(flyout_clean, sensors[20,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[20,1],".png")
save_as_image(x, path = file)
```



```{r}
dat_fly<-by_sensor_sort2(flyout_clean, sensors[21,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[21,1],".png")
save_as_image(x, path = file)
```


```{r}
dat_fly<-by_sensor_sort2(flyout_clean, sensors[22,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix_xray(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix_xray(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[22,1],".png")
save_as_image(x, path = file)
```


```{r}
#Energetic Particle Sensor LEO & L1
dat_fly<-by_sensor_sort2(flyout_clean, sensors[23,1])
x<-dat_fly %>%
  flextable() %>%
  color(j = 2:ncol(dat_fly), color = colormatrix_energetic_particle_LEO(dat_fly)) %>%
  bg(j = 2:ncol(dat_fly), bg = colormatrix_energetic_particle_LEO(dat_fly)) %>%
  align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[23,1],".png")
save_as_image(x, path = file)
```


```{r}
#Energetic Particle Sensor GEO - Low energy electrons and protons
dat_fly<-by_sensor_names(flyout_clean, sensors[24,1])
x<-dat_fly %>%
  flextable() %>%
  color(j = 2:ncol(dat_fly), color = colormatrix_energetic_particle_GEO_low(dat_fly)) %>%
  bg(j = 2:ncol(dat_fly), bg = colormatrix_energetic_particle_GEO_low(dat_fly)) %>%
  align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[24,1],".png")
save_as_image(x, path = file)
```


```{r}
#Energetic Particle Sensor GEO - High energy electrons and protons
dat_fly<-by_sensor_names(flyout_clean, sensors[25,1])
x<-dat_fly %>%
  flextable() %>%
  color(j = 2:ncol(dat_fly), color = colormatrix_energetic_particle_GEO_high(dat_fly)) %>%
  bg(j = 2:ncol(dat_fly), bg = colormatrix_energetic_particle_GEO_high(dat_fly)) %>%
  align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[25,1],".png")
save_as_image(x, path = file)
```


```{r}
#Energetic Particle Sensor GEO - Very high energy protons
dat_fly<-by_sensor(flyout_clean, sensors[26,1])
x<-dat_fly %>%
  flextable() %>%
  color(j = 2:ncol(dat_fly), color = colormatrix_energetic_particle_GEO_high(dat_fly)) %>%
  bg(j = 2:ncol(dat_fly), bg = colormatrix_energetic_particle_GEO_high(dat_fly)) %>%
  align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[26,1],".png")
save_as_image(x, path = file)
```


```{r}
#Energetic Particle Sensor GEO - Energetic heavy ions
dat_fly<-by_sensor(flyout_clean, sensors[27,1])
x<-dat_fly %>%
  flextable() %>%
  color(j = 2:ncol(dat_fly), color = colormatrix_energetic_particle_GEO_high(dat_fly)) %>%
  bg(j = 2:ncol(dat_fly), bg = colormatrix_energetic_particle_GEO_high(dat_fly)) %>%
  align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[27,1],".png")
save_as_image(x, path = file)
```


```{r}
#Magnetometer
dat_fly<-by_sensor(flyout_clean, sensors[28,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix_mag(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix_mag(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[28,1],".png")
save_as_image(x, path = file)
```



```{r}
#Plasma Analyzer
dat_fly<-by_sensor(flyout_clean, sensors[29,1])
x<-dat_fly %>%
    flextable()%>%
    color(j = 2:ncol(dat_fly), color = colormatrix2(dat_fly)) %>%
    bg(j = 2:ncol(dat_fly), bg = colormatrix2(dat_fly)) %>%
    align(j=2:ncol(dat_fly), align = "center", part = "header") %>%
    width(j = 1, width = 7) %>%
    width(j = 2:ncol(dat_fly), width = 5) %>%
    align(j= 2:ncol(dat_fly), align = "center", part = "header") %>%
    bold(part = "header") %>%
    fontsize(size = 11, j = 1) %>%
    fontsize(size = 5, j = 2:ncol(dat_fly)) %>%
    padding(padding.top = 2, part = "all") %>%
    padding(padding.bottom = 2, part = "all") %>%
    bold(j = 1)
file<-paste0("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/", sensors[29,1],".png")
save_as_image(x, path = file)
```